\documentclass[main.tex]{subfiles}
\title{Caitlin's lemony limoncello cookies}

\begin{document}

\maketitle

\begin{abstract}
A colleague of mine used to bake these cookies and bring them into the office every summer. She shared lots of delicious baking with us and I noticed that, of all of her cookie recipes, these were the quickest to be gobbled up. 
\end{abstract}

\section{Ingredients}

\vspace*{-\baselineskip}
\begin{table}[ht]
	\begin{tabularx}{\textwidth}{>{\hsize=0.333\hsize}X>{\bf\hsize=1\hsize}X}
	\unit[1]{cup} & candied lemon peel, finely chopped\\
	\unit[\nicefrac{1}{4}]{cup} & limoncello \\
	\unit[3\nicefrac{1}{3}]{cups} & plain flour\\
	\unit[1]{tsp} & baking soda\\
	\unit[1]{tsp} & baking powder\\
	\unit[\nicefrac{1}{2}]{tsp} & salt\\
	\unit[3]{tsp} & cornstarch\\
	\unit[1\nicefrac{1}{2}]{cups} & unsalted butter, softened\\
	\unit[1]{cup} & granulated sugar \\
	\unit[\nicefrac{2}{3}]{cup} & packed light-brown sugar \\
	\unit[3]{tbsp} & lemon zest (from about \unit[5]{} medium lemons)  \\
	\unit[2]{} & large eggs \\
	\unit[3]{tsp} & lemon extract\\
	\unit[2]{cups} & white chocolate chips \\
	\end{tabularx}
\end{table}

\section{Instructions}

\begin{enumerate}
    \item Preheat the oven to \unit[180]{\textdegree C} / \unit[350]{\textdegree F} and line your baking trays with baking paper.
    \item In a mixing bowl, toss together the candied lemon peel and limoncello. Set these aside while you mix the remaining ingredients. 
    \item Use an electric mixer to cream together butter, granulated sugar, brown sugar and lemon zest (combine these until they turn creamy, rather than continuing until they are pale and fluffy). 
    \item Mix in the eggs, then the lemon extract. With mixer set on low speed, slowly incorporate the dry ingredients before adding the white chocolate chips.
    \item Drain the lemon peel (there may not be a lot of liquid left) and mix in the lemon peel as well.
    \item Scoop the dough out \unit[2\nicefrac{1}{2}]{tbsp} at a time. Space the dollops of cookie dough a couple of inches apart as they will spread. 
    \item Bake the cookies for 10--12 minutes (the cookies should look slightly under-baked as they will continue to cook after they are removed the oven). Allow the cookies to cool for 2 minutes on the baking sheet before transferring them to a wire rack to cool.
\end{enumerate}
% \unit[325]{\textdegree F}

\end{document}
