\documentclass[main.tex]{subfiles}
\title{Caitlin's vegetable paella }

\begin{document}

\maketitle

\begin{margintable}
\begin{tabularx}{\textwidth}{WZ}
Time  & Serves\\ 
\midrule
50 min & 2
\end{tabularx}
\end{margintable}

\begin{abstract}
My sister decided to make this Yotam Ottolenghi recipe for our family when she was a tween and she dispatched my Dad to the grocery store on a quest to find saffron threads. It was a delicious experiment but rather too pricey so we've since omitted the saffron threads. Either I've forgotten how good it is with saffron in it, or it works well without it.
\end{abstract}

\section{Ingredients}

\vspace*{-\baselineskip}
\begin{table}[ht]
	\begin{tabularx}{\textwidth}{>{\hsize=0.333\hsize}X>{\bf\hsize=1\hsize}X}
	\unit[3]{tbsp} & olive oil\\
	\unit[\nicefrac{1}{2}]{} & white onion, finely chopped \\
	\unit[2]{} & small peppers, \unit[1]{} red and \unit[1]{} yellow, cut into strips\\
	\unit[\nicefrac{1}{2}]{} & small fennel bulb, cut into strips\\
	\unit[2]{} & garlic cloves, crushed\\
	\unit[2]{} & bay leaves \\
	\unit[\nicefrac{1}{4}]{tsp} & smoked paprika \\
	\unit[\nicefrac{1}{2}]{tsp} & ground turmeric \\
	\unit[\nicefrac{1}{4}]{tsp} & cayenne pepper \\
	\unit[150]{g} & Calasparra rice (or another paella rice) \\
	\unit[100]{ml} & sherry \\
	\unit[1]{tsp} & saffron threads (can be omitted) \\
	\unit[450]{ml} & boiling vegetable stock \\
	\unit[200]{g} & shelled broad beans (fresh or frozen) \\
	\unit[12]{} & mini plum tomatoes, halved \\
	\unit[5]{} & small grilled artichokes in oil from a jar, drained and quartered\\
	\unit[15]{} & pitted Kalamata olives, crushed or halved\\
	\unit[2]{tbsp} & roughly chopped parsley \\
	\unit[4]{} & lemon wedges \\
	& salt, to taste
	\end{tabularx}
\end{table}

\section{Instructions}

\begin{enumerate}
    \item Heat up the olive oil in a paella pan, or a large shallow frying pan, and gently fry onions 5 min. Add the peppers and fennel and continue to fry on a medium heat for about 6 min, or until soft and golden. Add the garlic and cook for a further minute.
    \item Add the bay leaves, paprika, turmeric and cayenne to the vegetables and stir well. Then add the rice and stir thoroughly for 2 min before adding the sherry and saffron. Boil down for a minute, then add the stock and \unit[\nicefrac{1}{3}]{tsp} salt. Reduce the heat to the minimum and simmer very gently for 20 min (or until most of the liquid has been absorbed by the rice). Do not cover the pan and don't stir the rice during the cooking.
    \item Meanwhile, pour plenty of boiling water over the broad beans in a bowl and leave for a minute, then drain well and leave to cool down. Now squeeze each bean gently to remove the skin and discard it.
    \item Remove the paella pan from the heat. Taste and add more salt if needed but without stirring the rice and vegetables much. Scatter the tomatoes, artichokes and broad beans over the rice and cover the pan tightly with foil. Leave to rest for 10 minutes.
    \item Take off the foil. Scatter the olives on top of the paella and sprinkle with parsley. Serve with wedges of lemon.
\end{enumerate}
Possible substitutions (with adjustment to the cooking times): carrots, courgettes, peas and sugar snaps.
% \unit[325]{\textdegree F}

\end{document}










