\documentclass[main.tex]{subfiles}
\title{Caitlin's lemon yoghurt cake}

\begin{document}

\maketitle

\begin{abstract}
The cake is taken from David Lebovitz’s blog and he recommends serving it with a lemon glaze and a fruit comp\^{o}te. I quite like having it with a dollop of Greek yoghurt and vanilla poached apricots as an alternative to the lemon glaze.
\end{abstract}

\section{Ingredients}

\subsection{For the cake}
\vspace*{-\baselineskip}
\begin{table}[ht]
	\begin{tabularx}{\textwidth}{>{\hsize=0.333\hsize}X>{\bf\hsize=1\hsize}X}
	\unit[1\nicefrac{1}{2}]{cups} & plain flour\\
	\unit[1]{tsp} & baking powder\\
	\unit[\nicefrac{1}{2}]{tsp} & baking soda\\
	\unit[\nicefrac{1}{2}]{tsp} & salt\\
	\unit[1\nicefrac{1}{2}]{cups} & sugar\\
	\unit[1]{cup} & plain yoghurt\\
	\unit[\nicefrac{1}{2}]{cup} & vegetable oil \\
	\unit[2]{} & large eggs, at room temperature \\
	\unit[2]{tbsp} & lemon juice\\
	& zest of 2 lemons
	\end{tabularx}
\end{table}

\subsection{For the lemon glaze\dots}
\vspace*{-\baselineskip}
\begin{table}[ht]
	\begin{tabularx}{\textwidth}{>{\hsize=0.333\hsize}X>{\bf\hsize=1\hsize}X}
	\unit[1\nicefrac{1}{2}]{cups} & icing sugar\\
	\unit[3]{tbsp} & lemon juice\\
	\end{tabularx}
\end{table}

\subsection{\dots or for the vanilla poached apricots}
\vspace*{-\baselineskip}
\begin{table}[ht]
	\begin{tabularx}{\textwidth}{>{\hsize=0.333\hsize}X>{\bf\hsize=1\hsize}X}
	\unit[1]{} & vanilla pod\\
	\unit[250]{ml} & water\\
	\unit[150]{g} & sugar\\
	\unit[8]{} & apricots\\
	\end{tabularx}
\end{table}

\section{Instructions}

\begin{enumerate}
    \item Preheat the oven to \unit[180]{\textdegree C} / \unit[350]{\textdegree F} and and butter a \unit[9]{in} (\unit[23]{cm}) cake pan, lining the bottom with baking paper.
    \item Whisk together the flour, baking powder, baking soda and salt.
    \item In a large bowl, whisk together the sugar, yoghurt, vegetable oil, eggs, lemon juice and zest until smooth.
    \item Stir the dry ingredients (roughly \nicefrac{1}{3} at a time) into the yoghurt mixture. Each time, mix just until the dry ingredients are completely incorporated. 
    \item Scrape the batter into the cake pan and bake for 40 minutes, or until a toothpick inserted into the centre of the cake comes out clean.
    \item Let the cake cook for 15 minutes, then run a knife around the tin to loosen it and tip the cake out of the pan. Remove the baking paper and let the cake cool completely, right side up, on a wire rack.
    \item To glaze the cake, mix the icing sugar and lemon juice until smooth then then pour it in the centre of the top of the cake. Use a spatula to spread it gently to the edges, allowing the glaze to drop down the side.
    \item Alternatively, serve the cake with a dollop of Greek yoghurt and some vanilla poached apricots. To poach the apricots, you should split the vanilla pod lengthways and scrape the seeds into a pan with \unit[250]{ml} water. Slowly bring this to a boil, while you halve the apricots and remove their stones. When the syrup boils, turn it down to a very low simmer and add the apricot halves. Cover the pan and simmer for 5--7 minutes. Take the pan off the heat shortly before the apricots are fully cooked, remove the lid and leave the apricots to cool in the syrup.
\end{enumerate}

\end{document}

