\documentclass[main.tex]{subfiles}
\title{Lyuba's unapologetically inauthentic pizza}

\begin{document}

\maketitle

\begin{margintable}
\begin{tabularx}{\textwidth}{WZ}
Time  & Serves\\ 
\midrule
60 min & 2--3
\end{tabularx}
\end{margintable}

\begin{abstract}
Pizza is a Hill View Road party staple---I make the dough and the tomato sauce in advance and then everyone builds their own. Peppers and various antipasti are always popular as toppings. One of our 2020 lockdown successes was aubergine, goats cheese, red onion and olives. Another great combination is mushrooms and pancetta.
\linebreak
Recipe adapted from BBC Good Food.
\end{abstract}

\section{Ingredients}

\subsection{For the base}
\vspace*{-\baselineskip}
\begin{table}[ht]
	\begin{tabularx}{\textwidth}{>{\hsize=0.333\hsize}X>{\bf\hsize=1\hsize}X}
	\unit[300]{g} & strong bread flour\\
	\unit[1]{tsp} & instant yeast\\
	\unit[1]{tsp} & salt\\
	\unit[1]{tbsp} & olive oil\\
	\unit[200]{ml} & warm water\\
	\end{tabularx}
\end{table}

\subsection{For the tomato sauce}
\vspace*{-\baselineskip}
\begin{table}[ht]
	\begin{tabularx}{\textwidth}{>{\hsize=0.333\hsize}X>{\bf\hsize=1\hsize}X}
	\unit[100]{ml} & tomato passata\\
	\unit[1]{tbsp} & dried oregano or mixed herbs\\
	\unit[]{} & dash of hot sauce\\
	\unit[]{} & sugar, salt and pepper, to taste\\
	\end{tabularx}
\end{table}

\subsection{For the toppings}
\vspace*{-\baselineskip}
\begin{table}[ht]
	\begin{tabularx}{\textwidth}{>{\hsize=0.333\hsize}X>{\bf\hsize=1\hsize}X}
	\unit[125+]{g} & grated mozzarella \\
	\unit[]{} & delicious pizza toppings \\
	\end{tabularx}
\end{table}

\section{Instructions}

\begin{enumerate}
    \item Heat the oven at \unit[240]{\textdegree C}. Yes, that high. That`s \unit[220]{\textdegree C} fan or gas mark 8.
    \item Stir the dry ingredients together for the base, make a well in the middle and add the oil and water. Combine with a wooden spoon and then knead.\marginnote{You’re aiming for a smooth dough which doesn't stick to your hands, holds its shape when dropped from above, and has the texture of the soft of your ear.} Cover and set aside. You can leave it to rise, but it`s not essential (and I certainly don`t).
    \item Roll out two pizza bases so they would fit onto your two preferred baking trays. Poke them with a fork to avoid air bubbles forming. Bake the bases without any toppings for 4--5 minutes. This is to avoid undercooked dough later.
    \item Meanwhile, make the tomato sauce, which is essentially just seasoned passata. I like adding the tiniest dash of hot sauce along with the herbs. I also like to only smear the pizza base with a bit of tomato, but you can up the quantities for a more authentic tomato base.
    \item Once your blind bake is done, brush the tomato sauce on top of each pizza and add the grated mozzarella\marginnote{Fresh mozzarella will make your pizza soggy, so make sure you use the grated stuff (or another type of cheese).}. Add the rest of your toppings on top of the cheese. Bake until done, usually 12--15 minutes, depending on how overloaded your pizza is.
	
\end{enumerate}

% \unit[325]{\textdegree F}

\end{document}


