\documentclass[main.tex]{subfiles}
\title{Lyuba's impossibly thin pancakes}

\begin{document}

\maketitle

\begin{margintable}
\begin{tabularx}{\textwidth}{WCZ}
Time  & Serves\\ 
\midrule
20 min & 2--3
\end{tabularx}
\end{margintable}

\begin{abstract}
My mother makes the thinnest, softest pancakes imaginable. My version is a fair approximation of hers, I think, especially since the wisdom she bestowed upon me was to ``mix enough milk, egg and flour until it looks right''. The real trick, she told me once, was to mix a very loose batter and to fry it over high heat for as little time as possible. I still have no idea what her milk-to-egg-to-flour ratio is though.
\linebreak
Recipe adapted from BBC Good Food.
\end{abstract}

\section{Ingredients}

\vspace*{-\baselineskip}
\begin{table}[ht]
	\begin{tabularx}{\textwidth}{>{\hsize=0.333\hsize}X>{\bf\hsize=1\hsize}X}
	\unit[100]{g} & plain flour\\
	\unit[]{} & pinch of salt\\
	\unit[2]{} & eggs\\
	\unit[\nicefrac{1}{2}]{tsp} & vanilla paste\\
	\unit[350]{ml} & milk\\
	\end{tabularx}
\end{table}

\section{Instructions}

\begin{enumerate}
    \item Mix the flour and salt together. Make a well in the middle. Add the eggs, oil, vanilla\marginnote{The easiest way to work with vanilla paste is to preheat your measuring spoon in a cup of boiling water first.} and a bit of the milk. Whisk into a smooth thick batter. 
    \item Slowly whisk the rest of the milk in. If you add all of the milk at the start, it’s much harder to get rid of any flour bubbles.
    \item The trick\marginnote{Make sure your frying pan is hot before you start frying the pancakes. And invest in a pancake pan if you can!} to frying thin, soft pancakes is to do it at a high temperature for a short time. People often say to cook the pancakes for 30 seconds per side, but I find it’s more like 20. If you have any excess batter, pour it back into the batter bowl rather than making an unnecessarily thick pancake. Pans will vary but I find I have to grease mine after every two or three pancakes.
    \item Serve with your choice of jams and spreads, including savoury ones if you're feeling adventurous! Honey and crushed walnuts are a Bulgarian staple.
	
\end{enumerate}

% \unit[325]{\textdegree F}

\end{document}

